---
title: "Simple document"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    ##overview of the document with folding code blocks
---

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
```


I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
##"opt + command + I" as the key stroke
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r round(mean(samp),2)`.

# Section 3
## plot from last time
This is going to make a plot! First I generate a dataframe, then use `ggplot` to make a scatterplot and a histogram.

```{r chunk_scatterplot}
plot_df = 
  tibble(
    x = rnorm(n=1000),
    y = 1 + 2 * x + rnorm(n=1000)
  )

ggplot(plot_df, aes(x=x, y=y)) + geom_point()
```

```{r chunk_histogram}
ggplot(plot_df, aes(x=x)) + geom_histogram()
```


## plot for learning assessment
This is a quick solution to the Learning Assessment

```{r}
la_df = 
  tibble(
    norm  = rnorm(n=500, mean=1),
    logical = norm>0,
    abs_norm = abs(norm)
  )

ggplot(la_df, aes(x=abs_norm)) + geom_histogram()
```

* The mean of the sample is `r mean(pull(la_df, norm))`
* The median of the sample is `r median(pull(la_df, norm))`
* The median of the sample is `r median(pull(la_df, norm))`

1.  Numbered list item 1
1.  Number item 2.